Brownian dynamics simulation of cytoplasmic dynein's powerstroke reproduces bidirectional stepping

### 2019-01-03 papers/paper/paper.tex
Add 2 paragraphs to results section on angle plots

\begin{figure}[tbhp]
  \centering
  \begin{subfigure}[]{0.8\columnwidth}\caption{}\vspace{5pt}\includegraphics[width=\columnwidth]{figures/winch-powerstroke-cartoon}\end{subfigure}\vspace{10pt}\\
  \begin{subfigure}[]{0.5\columnwidth}\caption{}\includegraphics[width=\columnwidth]{../../plots/bothbound_stroke_angles_bd}\end{subfigure}%
  \begin{subfigure}[]{0.5\columnwidth}\caption{}\includegraphics[width=\columnwidth]{../../plots/bothbound_stroke_angles_md}\end{subfigure}\\
  \begin{subfigure}[]{0.5\columnwidth}\caption{}\includegraphics[width=\columnwidth]{../../plots/bothbound_stroke_tailx_positions}\end{subfigure}%
  \begin{subfigure}[]{0.5\columnwidth}\caption{}\includegraphics[width=\columnwidth]{../../plots/bothbound_stroke_taily_positions}\end{subfigure}\\
  \begin{subfigure}[]{0.5\columnwidth}\caption{}\includegraphics[width=\columnwidth]{../../plots/bothbound_long_stroke_angles_bd}\end{subfigure}
  \caption{\textbf{Dynein model exhibits powerstroke, not winch, dynamics.} \textit{A. left: } Schematic of the winch mechanism. On free MTBD binding, linker swing in the just-bound head pulls the tail and cargo in the direction of the just-bound MTBD. \textit{A. right: } Schematic of the powerstroke mechanism. On free MTBD binding, linker swing pushes the just-bound head and tail domains towards the minus-end of the MT and alters the just-bound stalk domain's angle with the MT. \textit{b.) } Just-bound MTBD stalk angle relative to MT axis as a function of time since MTBD binding along with MTBD angle equilibrium (blue dotted line). \textit{c.) } Just-bound head angle, along with prestroke equilibrium (red dotted line) and poststroke equilibrium (blue dotted line). \textit{d.) } Change in tail domain x coordinate since MTBD binding. \textit{e.) } Value of tail domain y coordinate. All values sampled every $10 ns$. \textit{f.) } Just-bound MTBD stalk angle over the entirety of the post-powerstroke state, sampled every 1 $\mu s$. All values plotted as mean $\pm$ SD.}
\label{fig:stroke}
\end{figure}

Describe fig:stroke results here.
The transition rate from pre->post powerstroke compares roughly with MD simulations of the powerstroke \cite{mdstroke}. - is this actually true?

@@

One of the main advantages of our study is that it provides high spatial and temporal information about the model's behavior, which is currently unavailable for real dynein. This allows us to study mechanistic questions about how dynein walks. Our model appears to generate motion using the powerstroke mechanism long-theorized to account for dynein's motion\cite{mallikps, burgessknight, robertspowerstroke, burgess-paper} (CITE MORE). As our model transitions from the so-called pre-powerstroke to post-powerstroke state it increases its head angular spring energy from a shifting motor equilibrium angle; it relaxes this high motor energy by rotating its stalk towards the minus-end of the MT, pulling the motor and tail domains with it. This increase in head spring energy is roughly analogous to the high-energy state of the head of real dynein after MTBD binding induces Pi rejection and linker swing \cite{MANY-CITATIONS-HERE}. The stalk angle remains displaced from equilibrium until the next unbinding. Our simulations support the idea that a powerstroke-like mechanism also occurs in real dynein, where angular displacement of the just-bound stalk pulls the motor and tail domains forward.\\

This model contrasts with another theory on the dynein step called the winch mechanism \cite{carterwinch, uenoem, sarlahmodel, nicastro, kinoshitaPSwinch} (note: literature uses the term ``winch'' in different ways; we use the definitions from \textit{Lippert et. al} \cite{lippert}). According to this model, on MTBD rebinding, linker swing puts the just-bound head in a high energy state, just like in the powerstroke mdoel. However, to relieve this tension the motor instead ``winches'' its tail domain downwards in the direction of the stalk, resulting in a tail which is closer to the MT and further forward. To our knowledge, no previous simulation has tested the physical feasibility of either the winch or powerstroke models. Although our model is a minimal depiction which does not take into account the acute dynamics of the whole motor, its ability to reproduce the dynamics of the real dynein suggests that it may have some bearing on how the real dynein walks. In particular, this model spontaneously exhibits the powerstroke mechanism, suggesting that the powerstroke mechanism is both feasible for the dynein complex to generate and sufficient to explain much experimental data. Although this does not rule out the winch mechanism as an explanation, we believe that the lack of any winch-like behavior in our simulation is meaningful. Indeed during displacement our model's tail domain actually moves away from the microtubule, the opposite of the winch's prediction. Further theoretical studies demonstrating the feasibility and sufficiency of the winch mechanism are needed.\\

>>>>

\begin{figure}[tbhp]
  \centering
  \begin{subfigure}[]{0.8\columnwidth}\caption{}\vspace{5pt}\includegraphics[width=\columnwidth]{figures/winch-powerstroke-cartoon}\end{subfigure}\vspace{10pt}\\
  \begin{subfigure}[]{0.5\columnwidth}\caption{}\includegraphics[width=\columnwidth]{../../plots/bothbound_stroke_angles_bd}\end{subfigure}%
  \begin{subfigure}[]{0.5\columnwidth}\caption{}\includegraphics[width=\columnwidth]{../../plots/bothbound_stroke_angles_md}\end{subfigure}\\
  \begin{subfigure}[]{0.5\columnwidth}\caption{}\includegraphics[width=\columnwidth]{../../plots/bothbound_stroke_tailx_positions}\end{subfigure}%
  \begin{subfigure}[]{0.5\columnwidth}\caption{}\includegraphics[width=\columnwidth]{../../plots/bothbound_stroke_taily_positions}\end{subfigure}\\
  \begin{subfigure}[]{0.5\columnwidth}\caption{}\includegraphics[width=\columnwidth]{../../plots/bothbound_long_stroke_angles_bd}\end{subfigure}
  \caption{\textbf{Dynein model exhibits powerstroke, not winch, dynamics.} \textit{A. left: } Schematic of the winch mechanism. On free MTBD binding, linker swing in the just-bound head pulls the tail and cargo in the direction of the just-bound MTBD. \textit{A. right: } Schematic of the powerstroke mechanism. On free MTBD binding, linker swing pushes the just-bound head and tail domains towards the minus-end of the MT and alters the just-bound stalk domain's angle with the MT. Data used for subfigures b-e are for all steps with a positive step size. \textit{b.) } Just-bound MTBD stalk angle relative to MT axis as a function of time since MTBD binding along with MTBD angle equilibrium (blue dotted line). \textit{c.) } Just-bound head angle, along with prestroke equilibrium (red dotted line) and poststroke equilibrium (blue dotted line). \textit{d.) } Change in tail domain x coordinate since MTBD binding. \textit{e.) } Value of tail domain y coordinate. All values sampled every $10 ns$. \textit{f.) } Just-bound MTBD stalk angle over the entirety of the post-powerstroke state, sampled every 1 $\mu s$. All values plotted as mean $\pm$ SD.}
\label{fig:stroke}
\end{figure}

We then examined how the model took its forward steps. Two existing theories for motion generation are depicted in Figure \ref{fig:stroke}.a. The winch model \cite{carterwinch, uenoem, sarlahmodel, nicastro, kinoshitaPSwinch, lippert}, on the left, predicts that the prestroke to poststroke transition causes the just-bound motor's head to act like a winch, pulling the tail domain down and forwards toward the microtubule. The powerstroke model \cite{mallikps, burgessknight, robertspowerstroke, burgess-paper}, on the right, predicts that the transition will cause a lever-like action of the just bound stalk, pulling the just bound motor's head and tail forward. The most notable differences between these two models are whether the stalk angle changes during the stroke \cite{lippert}, and whether the tail domain moves closer or further from the microtubule. Arrows indicate these predictions in Figure \ref{fig:stroke}.a.\\

The average change of motor angles and positions during the prestroke-to-poststroke transition is shown in subfigures \ref{fig:stroke}.b-e. Only positive steps were used for clarity. Subfigure \ref{fig:stroke}.b indicates the model's just-bound stalk experiences a consistent angular displacement after binding, rotating to point more towards the minus end of the MT. Interestingly, this transition takes the binding angle out of equilibrium. This transition is permanent once made, as shown in \ref{fig:stroke}.f, which shows the no change even up to a millisecond after binding. This forward transition of the head domain is accompanied by a forward displacement of the tail domain by roughly 12 $nm$, as shown in Figure \ref{fig:stroke}.d, and a displacement away from the microtubule by 5-8 $nm$, as shown in Figure \ref{fig:stroke}.e. This tail displacement takes roughly 300ns, which corresponds roughly to the prestroke-to-powerstroke transition time from MD \cite{mdstroke} (DOES IT ACTUALLY THOUGH? LOOK AGAIN). The motor angle is shown in Figure \ref{fig:stroke}.c to transition from the pre-stroke equilibrium to the post-stroke equilibrium in time with the stalk angle change. Taken together, this data indicates that our simulated dynein moves through a powerstroke-, not a winch-type mechanism. We hypothesize that the out of equilibrium state of the motor angle post-transition is highly energetic, and it is quicker for the model to re-equilibrate the high-energy state through pushing the motor forward in a powerstroke than winching the faraway bulky tail downwards.\\

@@

One of the main advantages of our study is that it provides high spatial and temporal information about the model's behavior, which is currently unavailable for real dynein. This allows us to study mechanistic questions about how dynein walks. Our model appears to generate motion using the powerstroke mechanism long-theorized to account for dynein's motion \cite{mallikps, burgessknight, robertspowerstroke, burgess-paper}. As our model transitions from the so-called pre-powerstroke to post-powerstroke state it increases its head angular spring energy from a shifting motor equilibrium angle; it relaxes this high motor energy by rotating its stalk towards the minus-end of the MT, pulling the motor and tail domains with it. This increase in head spring energy is roughly analogous to the high-energy state of the head of real dynein after MTBD binding induces Pi rejection and linker swing \cite{MANY-CITATIONS-HERE}. The stalk angle remains displaced from equilibrium until the next unbinding. Our simulations support the idea that a powerstroke-like mechanism also occurs in real dynein, where angular displacement of the just-bound stalk pulls the motor and tail domains forward.\\

This model contrasts with another theory on the dynein step called the winch mechanism \cite{carterwinch, uenoem, sarlahmodel, nicastro, kinoshitaPSwinch, lippert} (note: literature uses the term ``winch'' in different ways; we use the definitions from \textit{Lippert et. al} \cite{lippert}). According to this model, on MTBD rebinding, linker swing puts the just-bound head in a high energy state, just like in the powerstroke mdoel. However, to relieve this tension the motor instead ``winches'' its tail domain downwards in the direction of the stalk, resulting in a tail which is closer to the MT and further forward. To our knowledge, no previous simulation has tested the physical feasibility of either the winch or powerstroke models. Although our model is a minimal depiction which does not take into account the acute dynamics of the whole motor, its ability to reproduce the dynamics of the real dynein suggests that it may have some bearing on how the real dynein walks. In particular, this model spontaneously exhibits the powerstroke mechanism, suggesting that the powerstroke mechanism is both feasible for the dynein complex to generate and sufficient to explain much experimental data. Although this does not rule out the winch mechanism as an explanation, we believe that the lack of any winch-like behavior in our simulation is meaningful. Indeed during displacement our model's tail domain actually moves away from the microtubule, the opposite of the winch's prediction. Further theoretical studies demonstrating the feasibility and sufficiency of the winch mechanism are needed.\\
